Astrophysical calibration of gravitational-wave detectors

### 2015-04-24 docs/cosmic_cal.tex
Some minor changes, but importantly I have correctly the likelihood function definition to be consistent with what is (correctly) actually used

% Define the likelihood function we will be using
We consider that the measured data in any detector is defined as
%
\begin{equation}
  d^{k}(f)=\tilde{n}^{k}(f)+s\gws_{k}(f)
\end{equation}
%
where $\tilde{n}(f)$ is the Fourier transform of Gaussian noise drawn from a
distribution consistent with the power-spectral-density of the advanced
detector noise.  The likelihood function for application to discretely sampled
data is 
%
\begin{equation}
  p(\vec{d} | \vec{\theta}, \curlH, I) \propto \exp\Bigg[ 2\Delta
f\sum_{k>0}\frac{|\tilde{d}(f_{k}) - \tilde{h}(f_{k})|^{2}}{S(f_{k})}\Bigg]
\end{equation}
% 
where $\Delta f$ is the frequency resolution of the frequency domain data.

% describe what parameters we will be considering and their priors
We assume uniform prior distributions on the unknown nuisance parameters
$\phi_{\mathrm{c}},\psi$ on their standard ranges. The time of coalescence is
restricted to a prior range of $\pm 10$ msec around the true value.  Given our
assumption of an \ac{sGRB} counterpart and host galaxy, we treat the sky
position as exactly known. We also consider the cosine of the inclination angle to be drawn
from a zero-mean Gaussian with standard deviation $0.1$ consistent with an
uncertainty on \ac{sGRB} opening of XXX~\cm{What was exactly done here?}.  The
main parameter of interest, the calibration scale factor $s$ is assumed to have
a uniform prior distribution on the range $(0,2)$.

>>>>

% Define the likelihood function we will be using
We consider that the measured data in any detector is defined as
%
\begin{equation}
  \tilde{d}_{k}(f)=\tilde{n}_{k}(f)+s\gws_{k}(f,\vec{\theta})
\end{equation}
%
where $\tilde{n}(f)$ is the Fourier transform of Gaussian noise drawn from a
distribution consistent with the power-spectral-density of the advanced
detector noise.

\MP{Our aim is to estimate the marginal posterior probability distribution function (pdf)
for the unknown calibration scale factor. We use Bayes' theorem for which we need to define
a likelihood function and prior pdfs on the signal parameters being estimated. In this
analysis we use a nested sampling algorithm \cite{Skilling} to provide samples from the
marginal posteriors that we require.}
We use a Gaussian likelihood function given by
%
%\begin{equation}
%  p(\vec{d} | \vec{\theta}, \curlH, I) \propto \exp\Bigg[ 2\Delta
%f\sum_{k>0}\frac{|\tilde{d}(f_{k}) - \tilde{h}(f_{k})|^{2}}{S(f_{k})}\Bigg]
%\end{equation}
\begin{equation}
  p(\vec{d} | \vec{\theta}, \curlH, I) \propto \exp{\left[4\Delta f \sum_{k=1}^{N_{\rm det}}
  \sum_{i=i_{f_{\rm low}}}^{i_{f_{\rm high}}}\frac{\Re{\left\{ \tilde{d}^{*}_{k,i} \gws_{k,i}(\vec{\theta})
  - \frac{1}{2}\left(\gws^*_{k,i}(\vec{\theta})\gws_{k,i}(\vec{\theta}) + \tilde{d}^*_{k,i}\tilde{d}_{k,i}\right) \right\}}}{S_{k,i}}\right]}
\end{equation}
% 
where $\Delta f$ is the frequency resolution of the data, $S_k$ is the
$k^{\rm th}$ detector's one sided noise power spectral density, and the $i$ indices
increment over frequency with $i_{f_{\rm low}}$ and $i_{f_{\rm high}}$ corresponding to
the lower and upper range in frequencies used for our
analsysis. \MP{Need to say the
range of frequencies we integrate over, which I think was 50\,Hz to 1600\,Hz from looking
at Liam's code.} The source parameters, and the unknown scale factor, have been subsumed
into a vector $\vec{\theta}$.

% describe what parameters we will be considering and their priors
We assume uniform prior distributions on the unknown nuisance parameters
$\phi_{\mathrm{c}},\psi$ on the ranges $[0, 2\pi]$ and $[0, \pi/2]$ respectively.
The time of coalescence is
restricted to a prior range of $\pm 10$ msec around the true value.  Given our
assumption of an \ac{sGRB} counterpart and host galaxy, we treat the sky
position as exactly known. We also consider the cosine of the inclination angle to be drawn
from a zero-mean Gaussian with standard deviation $0.1$ consistent with an
uncertainty on \ac{sGRB} opening of XXX~\cm{What was exactly done here?}.  The
main parameter of interest, the calibration scale factor $s$ is assumed to have
a uniform prior distribution on the range $(0,2)$.
